Introducing Statistical Design of Experiments to SPARQL Endpoint Evaluation

### 2013-05-08 exp1/iswc2013.tex
Acknowledgements
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@536 43ef1190-90fd-4dd7-a769-d0121f02b80e
future work start
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@537 43ef1190-90fd-4dd7-a769-d0121f02b80e

\subsection{Fractional factorial experiment}

@@

@@

@@

>>>>

\subsection{Fractional factorial experiment}\label{sec:frac}

@@

The present experiment is very primitive in its choice of factors, and
we believe that the strategy employed to construct suitable
experiments will be the main determinant for the long-term feasibility
of this direction. One strategy will be to start with broad factors
such as ``Machine'' and refine them with experience. A more difficult
issue is how to address the problem of testing the whole SPARQL
language. We believe that the parameterization work inititated by
\cite{goerlitz2012splodge} with their SPLODGE system is a key
ingredient. They parameterized SPARQL queries in such a way they could
be autogenerated. One suggestion is to parameterize queries based on
the grammar, so that one factor becomes the number of e.g. UNIONs, and
the levels are chosen. One problem one will soon run into is that
parts of the language is recursive, e.g. a GroupGraphPattern can
consist of several GroupGraphPatterns. However, we believe that
pragmatic limits can be set, it is for example not of practical
interest to nest OPTIONALs to any great depth even if it is allowed by
the language.

We saw in section~\ref{sec:frac} that with a smaller experiment, fewer
interactions are significant, and so provides us with fewer clues to
assess the soundness of the experiment. This should be a focus of
further research.

Finally, we have only employed the simplest parts of the DoE
theory, what has been presented here is part of a much more general
formalism known as Orthogonal Arrays. The use of orthogonal arrays
allow for different numbers of levels, for much greater flexibility in
total run size, and for irregular designs that can provide a good fit
for the complex problem of SPARQL endpoint evaluations.

@@

Feasible doing millions of runs.

@@

Kjetil Kjernsmo would like to thank his main supervisor Martin Giese
for kind assistance in writing this paper. He would also like to
thank Steve Harris for his generous support in degrading his excellent
work on 4store.
